---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CopyDetect

<!-- badges: start -->
<!-- badges: end -->

The goal of CopyDetect is to compute several IRT and non-IRT based response similarity indices proposed in the literature for multiple-choice examinations such as the Omega index [(Wollack, 1997)](doi:10.1177/01466216970214002),Generalized Binomial Test [(van der Linden & Sotaridona, 2006)](doi:10.3102/10769986031003283),K index, K1 and K2 indices [(Sotaridona & Meijer, 2002)](doi:10.1111/j.1745-3984.2002.tb01138.x), M4 index [(Maynes,2014)](), and S1 and S2 indices [(Sotaridona & Meijer, 2003)](doi:10.1111/j.1745-3984.2003.tb01096.x).

## Installation

You can install the released version of CopyDetect from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("CopyDetect")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("czopluoglu/CopyDetect")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CopyDetect)
## basic example code
```


